---
title: "Week 6 Coding Lab"
author: "Travis Christy"
date: "11/15/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(palmerpenguins)
library(ggpubr)
library(broom)
```

### Part 1 Attach packages (done above)
  
  
### Part 2. A rank-based test example (Mann Whitney U)  

Create two sample vectors called gp_1 and gp_2. 
We use set.seed() here to create a “pseudorandom” sample, so that we all get the same samples – otherwise we’d all get something different! 
We use sample.int() to create random samples with integers from 1 to x, of size = ?, with replacement:

```{r}
set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

We ask: Is there evidence for a significant difference in ranks (medians) between the populations from which gp_1 and gp_2 were drawn?

First, always look at it (here, using the base R hist() function to create an exploratory histogram of each – fine if you’re only doing this for a quick look with a vector, but customization can be more challenging than in ggplot):

```{r}
hist(gp_1)
hist(gp_2)
```
If I want to compare ranks between gp_1 and gp_2, what are some reasons I might choose a rank-based test?
  
- Not clearly normally distributed from exploratory histograms
- Somewhat small sample size (n = 15 for each)
- I’ve decided that ranks (or, medians) are a more valuable metric to compare for these data.
  
  
Here, we’ll perform Mann-Whitney U to answer “Is there a significant difference in ranks (medians) between gp_1 and gp_2?” using the wilcox.test() function.

```{r}
my_mwu <- wilcox.test(gp_1, gp_2)
```
































